\subsection*{I am stuck. Where can I get help?}

If this F\+A\+Q does not contain your question, \href{http://git.libelektra.org/issues}{\tt please open an issue}. You can simply remove all template text and it is enough if the issue only contains your question. If you want you can \href{http://git.libelektra.org/issues/labels/question}{\tt label it as question}, but we can also categorize it for you.

Please do not waste too much time to find something out yourself. Information where people get stuck is valuable to improve Elektra and its documentation. Even if you find out directly after you posted the question\+: the pointer can be helpful for other people having the same problem.

\subsection*{Is this an actual problem or is it just me?}

In case of doubt \href{http://git.libelektra.org/issues}{\tt please open an issue}. If the question was already answered or is already in the documentation, we will simply point it out to you.

So do not worry too much, do not hesitate to ask any question. We welcome feedback, only then we can improve the documentation such as this F\+A\+Q!

\subsection*{What should I do if I found a bug?}

Please check the \href{http://git.libelektra.org/issues}{\tt issue tracker} if it has already been reported. If it has not, please \href{http://git.libelektra.org/issues/new}{\tt fill out the template}. If you are in doubt, please report it.

\subsection*{How can I contribute to Elektra?}

Due to the modular architecture we can accept nearly all contributions as plugins. Please only make sure that the R\+E\+A\+D\+M\+E.\+md clearly states the purpose and quality of the plugin. If you need, e.\+g., a plugin that crashes the process make sure that you tag ({\ttfamily infos/status}) it with {\ttfamily discouraged}.

Please start by reading here.

\subsection*{What is the Elektra's license?}

\hyperlink{doc_LICENSE_md}{New B\+S\+D license} which allows us to have plugins link against G\+P\+L and G\+P\+L-\/incompatible libraries. If you compile Elektra, e.\+g., with G\+P\+L plugins, the result is G\+P\+L.

\subsection*{Who are the authors?}

List of authors. 